Merging merges, more or less

### 2015-02-03 2015mergingmerges/section/03-Access.tex
ok

Indeed, if we have two graphs, $\forall g~g' : @Graph@.$
\begin{eqnarray*}
 & \filterR(\regex(g)) = \filterR(\regex(g')) \\
 \implies & \forall w. w \in \filterR(\regex(g)) \iff w \in \filterR(\regex(g')) \\
 \implies & \forall is. \exists t : @Trace@~g~is. \exists t' : @Trace@~g'~is. \\
          & \filterT(\flatten(t)) \in \filterR(\regex(g)) \\
          & \wedge~\filterT(\flatten(t')) \in \filterR(\regex(g')) \\
          & \wedge~\filterT t = \filterT t' \\
 \implies & \affable(t, t') \\
 \implies & \mathit{fusible}(g, g') \\
\end{eqnarray*}

>>>>

Indeed, if we have two graphs, $\forall g~g' : @Graph@.$
\begin{eqnarray*}
 & \filterR(\regex(g)) = \filterR(\regex(g')) \\
 \implies & \forall w. w \in \filterR(\regex(g)) \iff w \in \filterR(\regex(g')) \\
 \implies & \forall is. \exists t : @Trace@~g~is. \exists t' : @Trace@~g'~is. \\
          & \filterT(\flatten(t)) \in \filterR(\regex(g)) \\
          & \wedge~\filterT(\flatten(t')) \in \filterR(\regex(g')) \\
\end{eqnarray*}

But it is not necessarily true that these two traces $t$ and $t'$ have the same filtered flattening.
I \emph{think} it is true, because they have the same inputs, but I need to think about how to prove it.
Something about determinism.
\begin{eqnarray*}
          & \wedge~\filterT t = \filterT t' \\
 \implies & \affable(t, t') \\
 \implies & \mathit{fusible}(g, g') \\
\end{eqnarray*}

We can split the combinators into two types: value dependent and independent.
Filter, merge join and indices are value dependent, whereas map, append, zip, and so on are value independent.
Value independent combinators have the property that for all inputs, the trace can be determined solely by the length of the inputs, regardless of the values.

\subsubsection{Examples}
Going back to the original @app2@ example, let us compute its access pattern.
I use a simplified, canonical form here and discard the worker functions.

\begin{code}
app2 :: [(Bool,a)] -> [(Bool,a)]
app2 X
 = let F = filter X     :~ (XF?)*
       G = filter X     :~ (XG?)*
       H = append F G   :~ (XF?)*(XG?)*
   in  H
\end{code}
If we try to fuse @F@ and @G@, we start by finding the common parts, which is just @X@. Filtering both access patterns to only occurrences of @X@ leaves @X*@ and @X*@, which are trivially equal.
Therefore, @F@ and @G@ can be fused.

However, if we attempt to fuse @F@ with @H@, we must again find the intersection: this being @X@ and @F@.
We find that @F@'s filtered access pattern remains the same, @(XF?)*@, while @H@'s filtered access pattern is @(XF?)*X*@. These two regular expressions are not equal, and thus @F@ and @H@ may not be fused.

### 2015-02-03 2015mergingmerges/section/XX-RelatedWork.tex
ok

>>>>

\subsection{Solving out-of-order communication in Kahn Process Networks}
This is \cite{turjan2002compile}, resulting from a search about regular expressions and KPNs.
\emph{Compaan} is about converting signal processing Matlab code to KPNs.
Determine whether, for their given networks, reordering is necessary to limit buffers and deadlocks.
It looks like this only works for statically known polytope loops.

\subsection{Realtime Signal Processing}
This is \cite{reekie1995realtime} by Hideki John Reekie at UTS.
Very interesting work on Visual Haskell, a visual dataflow-esque representation of Haskell programs.
Talks about static and dynamic dataflow, but really just seems to be about the required combinators, and not compilation.
Rewrite-rules based optimisations, so only local information like map/map fusion etc.

\subsection{Requirements on the execution of Kahn process networks}
This is \cite{geilen2003requirements}.

Looks like this is directed at solving some problems in Parks\cite{parks1995bounded} where KPNs are scheduled in bounded memory, but has incorrect behaviour for some KPNs.
The incorrect behaviour is that ``local artificial deadlocks'' can occur, where a subset of the network cannot proceed as it requires a larger buffer, but other parts can still make progress.
Parks only deals with ``global artificial deadlocks'', where the entire network can make no progress.
As a result, the output may not be ``complete''.

Writing is normally non-blocking, but they have writing to a full buffer block.
Talks about using cycles to detect local deadlocks. 
Shows that process networks with channel bounds are deterministic - and our subset of KPN has all channels bounded by 1.
Their scheduling algorithm just enlarges the smallest full buffer whenever any sort of deadlock occurs.
